Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-03-27 source/main.tex
accelerated sgd, cvx, non-smoth v1

\newcommand{\eq}[1]{{Eq~(#1)}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}
\newcommand{\lkxcom}[1]{{\color{red}{#1}}}
\input{bmacros}
\newtheorem*{assumption*}{Assumption}

@@

%% Note for ICLR'20 paper
% \input{note_sec_problem}
% \input{note_sec_algorithm}
% \input{note_sec_part}
% \input{note_sec_q}

% converge proof
\input{sec_problem}
\input{sec_overview}
\newpage
% \input{sec_acceleratedFL}
% \input{sec_cvxnonsm}

@@

>>>>

\newcommand{\eq}[1]{{Eq~(#1)}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{remark}{Remark}
\newcommand{\lkxcom}[1]{{\color{red}{#1}}}

\newcommand{\ov}[1]{{\overline{\mathbf{#1}}}}
\input{bmacros}
\newtheorem*{assumption*}{Assumption}

@@

% converge proof
\input{sec_problem}
\input{sec_overview}

\input{sec_acceleratedFL}

@@

% paper

\begin{itemize}
	\item On Federated Learning of Deep Networks from Non-IID Data: Parameter Divergence and the Effects of Hyperparametric Methods: empirical evaluation 
	paper, the loss surface could be helpful.
	\item On the Linear Speedup Analysis of Communication Efficient Momentum SGD for Distributed Non-Convex Optimization: Non-convex, smooth, accelerated SGD, Full device particaption.
\end{itemize}
